\documentclass[11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem} % For custom list formatting

% Remove page numbers
\pagestyle{empty}

% Define custom section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries\raggedright}{}{0em}{}
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

% Custom formatting for contact info
\newcommand{\contactinfo}[3]{%
  \begin{center}
    \textbf{\Large #1}\\[5pt]
    #2 \textbar\ #3
  \end{center}
  \vspace{-10pt} % Adjust spacing after contact info
}

\begin{document}

% Contact Information
\contactinfo{Saragadma Vamshi}{Visakhapatnam, India \textbar\ iamvamsi0@gmail.com}{\textbar\ +91 9381721427}

% Summary
\section*{Summary}
Highly motivated and results-oriented Computer Science candidate with a strong foundation in AI-driven application development, particularly focusing on Large Language Models (LLMs) and conversational AI. Possessing foundational skills in prompt engineering, natural language processing, and integrating advanced AI APIs to create intelligent systems. Eager to apply and expand expertise in developing cutting-edge AI solutions, contributing to high-impact, innovative products within dynamic environments like the insurance sector, aligning with the company's vision for transformative innovation.

% Education
\section*{Education}
\begin{itemize}[leftmargin=*,labelsep=0.5em]
    \item \textbf{Bachelor of Technology, Computer Science} \hfill Expected: 2025
    Maharaj Vijayaram Gajapathi Raj College of Engineering
    \item \textbf{Diploma in Computer Science} \hfill 2022
    Government Polytechnic, Anakapalli
\end{itemize}

% Skills
\section*{Skills}
\begin{itemize}[leftmargin=*,labelsep=0.5em]
    \item \textbf{AI \& Machine Learning:} Large Language Models (LLMs), Natural Language Processing (NLP), Prompt Engineering, Data Preprocessing, Model Evaluation, TensorFlow (Foundational), PyTorch (Foundational), Scikit-learn, Pandas, NumPy, Python
    \item \textbf{Web Technologies:} React.js, Node.js, Express.js, JavaScript, HTML, CSS
    \item \textbf{Databases:} MongoDB, MySQL, SQLite
    \item \textbf{Tools \& Methodologies:} Git, GitHub, REST APIs, Data Structures & Algorithms, Linux
\end{itemize}

% Projects
\section*{Projects}
\vspace{-5pt} % Adjust spacing
\begin{itemize}[leftmargin=*,labelsep=0.5em]
    \item \textbf{Social Media Scribe (AI-Powered Conversational Content Generation Platform)} \hfill Project Live Link: \underline{Social Media Scribe}
    \begin{itemize}[leftmargin=1.5em]
        \item Designed and implemented an AI-driven platform for generating tailored social media content, demonstrating foundational experience in Natural Language Generation (NLG) and prompt engineering principles.
        \item Integrated and optimized Large Language Model (LLM) APIs (e.g., OpenAI/similar) to produce contextually relevant and engaging text, focusing on dynamic content rendering for diverse platforms.
        \item Developed modular JavaScript components to handle complex user input, asynchronously communicate with AI APIs, and manage dynamic content, applying principles analogous to dialogue state management and effective sales response generation in conversational AI.
        \item Architected the backend to ensure robust communication with AI services, securing user access with JWT tokens and ensuring data integrity and suitability for AI inputs and outputs, critical for model performance.
        \item \textit{Technologies Used:} React.js, Node.js, JavaScript, REST API, LLM APIs, JWT Token, MongoDB.
    \end{itemize}

    \item \textbf{Course Selling Application}
    \begin{itemize}[leftmargin=1.5em]
        \item Designed and developed a full-stack persistent course-selling application, enabling efficient creation, tracking, and management of courses for users and administrators.
        \item Structured comprehensive database schemas for user, admin, and course details, optimizing data storage and retrieval processes for scalability.
        \item Implemented secure login and signup functionalities using JWT tokens for robust authentication and authorization.
        \item \textit{Technologies Used:} Express.js, MongoDB, JWT Token.
    \end{itemize}
\end{itemize}

% Interests & Languages
\section*{Interests \& Languages}
\begin{itemize}[leftmargin=*,labelsep=0.5em]
    \item \textbf{Interests:} Actively exploring new advancements in AI and Machine Learning, with a keen focus on conversational AI, natural language understanding, LLM fine-tuning, and efficient model deployment strategies, particularly within the FinTech and Insurance domains.
    \item \textbf{Languages:} Fluent in English, Native in Telugu.
\end{itemize}

\end{document}