\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{
    a4paper,
    top=0.75in,
    bottom=0.75in,
    left=0.75in,
    right=0.75in
}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{textcomp} % Crucial for common symbols

% Set page style to empty to remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt} % space before and after section title

% Custom commands for resume structure
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4}
    \end{tabular*}
}
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, noitemsep, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Saragadma Vamshi} \\ \vspace{4pt}
    Visakhapatnam, India $|$ +91-9381721427 $|$ \href{mailto:iamvamsi0@gmail.com}{\underline{iamvamsi0@gmail.com}} \\
    \href{https://linkedin.com/in/yourprofile}{\underline{LinkedIn}} $|$ \href{https://github.com/yourprofile}{\underline{GitHub}} % Placeholder links as original not provided
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
A highly motivated Computer Science graduate with a strong foundation in fullstack development, specializing in \textbf{React.js}, \textbf{Node.js}, and \textbf{Express.js}. Passionate about designing and building high-quality, intuitive software that enhances user experience and solves real-world workflow challenges, particularly in healthcare technology. Proven ability to integrate \textbf{AI functionality} into applications and optimize performance. Eager to contribute to a fast-paced, user-centered startup environment like Bemlo, driving impactful change through innovative solutions.

%-----------EDUCATION-----------
\section*{Education}
\resumeSubHeadingListStart
    \resumeSubheading
    {Maharaj Vijayaram Gajapathi Raj College of Engineering}{Vizianagaram, India}
    {Bachelor of Technology, Computer Science}{Expected 2025}
    \resumeSubheading
    {Government Polytechnic, Anakapalli}{Anakapalli, India}
    {Diploma in Computer Science}{2022}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section*{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{\textbf{Frontend Development:} React.js, HTML, CSS, JavaScript, Bootstrap}
    \item \small{\textbf{Backend Development:} Node.js, Express.js, Java}
    \item \small{\textbf{Databases:} MongoDB, MySQL, SQLite}
    \item \small{\textbf{Tools \& Concepts:} Git, GitHub, Linux, Data Structures \& Algorithms (DSA), REST API, Authentication (JWT), Performance Optimization, User-Centered Design}
\end{itemize}

%-----------PROJECTS-----------
\section*{Projects}
\resumeSubHeadingListStart
    \resumeSubheading
    {Social Media Scribe}{}
    {}
    {\href{http://grog-social-scribe.lovable.app/}{\underline{Project Live Link}}} % Preserving original link if active
    \resumeItemListStart
        \resumeItem{Developed an \textbf{AI-driven post generator} to create tailored content for various social media platforms, directly aligning with the integration of AI for enhanced user experience.}
        \resumeItem{Designed and implemented modular JavaScript and \textbf{React.js} components to handle user input, asynchronously communicate with \textbf{AI APIs}, and render dynamic content, focusing on intuitive user interactions.}
        \resumeItem{Secured user access with robust \textbf{JWT token}-based authentication and authorization mechanisms, ensuring data integrity and user privacy.}
        \resumeItem{Focused on transforming complex requirements into a delightful solution, emphasizing seamless navigation and a streamlined user journey.}
    \resumeItemListEnd

    \resumeSubheading
    {Course Selling App}{}
    {}
    {}
    \resumeItemListStart
        \resumeItem{Engineered a persistent course-selling application enabling efficient creation, tracking, and management of courses for users and administrators.}
        \resumeItem{Designed a structured database schema and implemented secure login/signup functionality using \textbf{JWT tokens} for robust user authentication.}
        \resumeItem{Utilized arrays, objects, and \textbf{optimized data structures} to ensure high performance and responsiveness, demonstrating an interest in system optimization.}
        \resumeItem{Developed a scalable backend using \textbf{Express.js} and \textbf{MongoDB}, emphasizing clean architecture and maintainability for future enhancements.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ADDITIONAL INFORMATION-----------
\section*{Additional Information}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{\textbf{Languages:} English (Fluent), Telugu (Native)}
    \item \small{\textbf{Interests:} Exploring frontend development (React.js), leveraging AI for practical user-centric solutions, problem-solving, and building performant applications.}
\end{itemize}

\end{document}